A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-10 tex/codatadp.tex
Refactor cyclic/bisimilar based on new definitions.

We present the calculus in three sections, shown in Figures~\ref{fig:cc-rules},~\ref{fig:ab-rules}, and~\ref{fig:split-rule}.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we will call an application of it to be \emph{non-terminal}),
or is $\bot$ (in which case we will call an application of it to be \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes a non-deterministic branching.
An application of a rule is \emph{redundant} if it is non-terminal and at least one branch in its conclusion does not add a new equality to $\Ec$.

@@

Figure~\ref{fig:cc-rules} gives the basic rules of our calculus.
Together with the rules \rn{Refl}, \rn{Symm}, \rn{Trans}, the rule \rn{Cong} computes the (upwards) congruence closure,
while the rules \rn{Unify$_1$} and \rn{Unify$_2$} together compute (downwards) unification.
In the unification rules, additional equalities are inferred based on the injectivity of constructors by \rn{Unify$_1$},
and failures to unify equated terms are recognized by \rn{Unify$_2$}.
The rule \rn{Conflict} recognizes when an equality and its negation both occur in $\Ec$, in which case $\Ec$ has no model.

\begin{figure}[t]
\centering
\begin{tabular}{c}
\rn{Cyclic}
\(
\inferrule{
  t : \tau
  \quad
  \tau \in \Data
  \quad
  \ttpath{\Ec}{\ec{t}}{\ec{t}} \neq \emptyset
}{
  \bot
}
\)
\\[3.7ex]
\rn{Bisimilar}
\(
\inferrule{
 t_1, t_2 : \tau
  \quad
 \tau \in \Codata
  \quad
 \tpath{\Ec}{\ec{t_1}} = \tpath{\Ec}{\ec{t_2}}\sigma \neq \emptyset
}{
 \Ec := \Ec, t_1 \teq t_2
}
\)
\end{tabular}
\caption{Rules for cyclicity and bisimilarity.
}
\label{fig:ab-rules}
\end{figure}

Before applying the rules in Figure~\ref{fig:ab-rules}, 
we assume that $\Ec$ is saturated with respect to the rules in Figure~\ref{fig:cc-rules}, that is,
no non-redudant application of one of its rules can be applied to $\Ec$.
When this is the case, it is easy to see that $\Ec$ induces an equivalence relation over $\tEc$ such that two terms $t_1$ and $t_2$ are equivalent if and only if $t_1 \teq t_2 \in \Ec$.
Thus, we will in the following consider $\Ec$ as a set of equivalence classes of terms. 
For term $t \in \tEc$, we will write $\ec{t}$ to denote the equivalence class in $\Ec$ that containing $t$.

To explain the rules in Figure~\ref{fig:ab-rules}, we introduce the following notions.
First, an edge $\ec{t_1} \rightarrow^{C}_n \ec{t_2}$ is a transition between two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ 
(which we will call its \emph{source} and \emph{destination} respectively),
labeled by a constructor $C$ and integer $n$.
We say that edge $\ec{t_1} \rightarrow^{C}_n \ec{t_2}$ is \emph{induced by $\Ec$} if and only if $C( \vec u ) \in \ec{t_1}$ for some $\vec u$ and $\ec{t_2} = \ec{u_n}$.
In other words, $t_1$ is equivalent to a $C$-application whose $n^{th}$ argument is equivalent to $t_2$.
A \emph{path} $p$ is a non-empty ordered list of edges $e_1, \ldots e_n$ such that the destination of $e_i$ is the source of $e_{i+1}$ for $i = 1, \ldots (n-1)$,
and the sources of $e_1, \ldots, e_n$ are distinct.
We say that path $p$ is \emph{induced by $\Ec$} if and only if each of its edges are induced by $\Ec$.
Notice that since $\Ec$ contains a finite set of equivalence classes, all paths induced by $\Ec$ have finite length.
We call the \emph{source} of a path is the source of its first edge, and the \emph{destination} of a path is the destination of its last edge.
We say a path $p$ is \emph{maximal} if its destination $\ec{t}$ is either
the source of an edge in $p$, 
or does not contain an application of a non-nullary constructor (including the case when $t$ is not of datatype/codatatype type).
The set $\ttpath{\Ec}{\ec{t_1}}{\ec{t_2}}$ is the smallest set containing all maximal paths with source $\ec{t_1}$ and destination $\ec{t_2}$ that are induced by $\Ec$.
The set $\tpath{\Ec}{\ec{t_1}}$ is the union of $\ttpath{\Ec}{\ec{t_1}}{\ec{t_2}}$ for all $t_2 \in \tEc$.
We will write, for instance, $\ec{t_1} \rightarrow^{C_1}_{n_1} \ec{t_2} \rightarrow^{C_2}_{n_2} \ec{t_3}$ 
as shorthand for the path containing an edge from $\ec{t_1}$ to $\ec{t_2}$, followed by one from $\ec{t_2}$ to $\ec{t_3}$.
%A set of paths is \emph{disjoint} if it does not contain two paths $p_1$ and $p_2$ such that $p_1 = p_2 \sigma$ for some $\sigma$.

The rule \rn{Cyclic} recognizes when a path exists from an equivalence class $\ec{t}$ to itself, as indicated
by the assumption $\ttpath{\Ec}{\ec{t}}{\ec{t}} \neq \emptyset$.
In this case, $\Ec$ entails that $t$ contains itself as a (strict) subterm,
and thus if $t$ is a datatype, $\Ec$ must be unsatisfiable.
The rule \rn{Bisimilar} recognizes when two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ having co-datatype type are observationally equivalent.
In this rule, $\sigma$ is a complete mapping over the equivalence classes that occur as sources in the edges of paths in $\tpath{\Ec}{\ec{t_2}}$.
The rule applies if $\tpath{\Ec}{\ec{t_1}}$ is comprised of the paths $p \sigma$ for each (and only) the paths $p \in \tpath{\Ec}{\ec{t_2}}$,
in which case $t_1$ must be equal to $t_2$.
We demonstrate an application of this rule concretely with the following example.

\begin{example}
Let $\const{C}$ be a constructor of type $\tau_1 \times \tau_2 \rightarrow \tau_2$,
and let $\Ec$ be the set $\{ x \teq \const{C}(y,\const{C}(y,x)) \}$.
After applying the rules in Figure~\ref{fig:cc-rules} to completion, the equivalence classes of $\Ec$ are
$\{ x, \const{C}(y,\const{C}(y,x)) \}$, $\{ \const{C}(y,x) \}$, and $\{ y \}$.
The sets $\tpath{\Ec}{\ec{x}}$ and $\tpath{\Ec}{\ec{\const{C}(y,x)}}$ are:
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l}
\{ & \ec{x} \rightarrow^{\const{C}}_1 & \ec{y}, & & & 
\{ & \ec{\const{C}(y,x)} \rightarrow^{\const{C}}_1 & \ec{y}, & & \\ 
   & \ec{x} \rightarrow^{\const{C}}_2 & \ec{\const{C}(y,x)} \rightarrow^{\const{C}}_1 & \ec{y},&  &
   & \ec{\const{C}(y,x)} \rightarrow^{\const{C}}_2 & \ec{x} \rightarrow^{\const{C}}_1 & \ec{y},& \\
   & \ec{x} \rightarrow^{\const{C}}_2 & \ec{\const{C}(y,x)} \rightarrow^{\const{C}}_2 & \ec{x} & \} &
   & \ec{\const{C}(y,x)} \rightarrow^{\const{C}}_2 & \ec{x} \rightarrow^{\const{C}}_2 & \ec{\const{C}(y,x)} & \}.
\end{array}\]
Thus, by the rule \rn{Bisimilar}
for the mapping $\sigma :=$ $\{ \ec{x} \mapsto \ec{\const{C}(y,x)}, \ec{\const{C}(y,x)} \mapsto \ec{x} \}$,
we may infer $x \teq \const{C}(y,x)$.
\qed
\end{example}

@@

\rem{Require : all co-datatypes either have infinite cardinality, or have cardinality 1.}

@@

Recall that the $\mu$-notation can be used to represent (possibly cyclic) values taken from an initial algebra, \rem{elaborate?} 
e.g. $\mu x. \const{C}( \const{0}, x )$ represents the infinite sequence $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
In this setting, a value can be viewed as a term-like structure where all subterms 
(which we will refer to as \emph{subvalues}) are either 
$\mu x. \const{C}( \vec v )$ for some constructor $\const{C}$ and subvalues $\vec v$
\footnote{We assume all values are well-typed. 
Here, the type of $\mu x. \const{C}( \vec v )$ and $x$ is the return type of $\const{C}$.}, or a variable $x$.
We will refer to values of this form as \emph{$\mu$-values}.
We say a $\mu$-value is \emph{closed} if it contains no free variables.
For convienience, we will represent the values of both datatypes and co-datatypes as closed $\mu$-values,
where the case of datatypes adds the restriction that none of its subvalues are variables.

>>>>

We present the calculus in three parts.
In the first part we compute the bidirectional closure of $\Ec$,
in the second part we make inferences based on cyclicity and bisimilarity,
and in the third part we (when necessary) split on the constructor type for various terms in $\tEc$.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we will call an application of it to be \emph{non-terminal}),
or is $\bot$ (in which case we will call an application of it to be \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes a non-deterministic branching.
An application of a rule is \emph{redundant} if it is non-terminal and at least one branch in its conclusion does not add a new equality to $\Ec$.

@@

\paragraph{Step 1: Compute Birectional Closure}
Figure~\ref{fig:cc-rules} gives the basic rules of our calculus.
Together with the rules \rn{Refl}, \rn{Symm}, \rn{Trans}, the rule \rn{Cong} computes the (upwards) congruence closure,
while the rules \rn{Unify$_1$} and \rn{Unify$_2$} together compute (downwards) unification.
In the unification rules, additional equalities are inferred based on the injectivity of constructors by \rn{Unify$_1$},
and failures to unify equated terms are recognized by \rn{Unify$_2$}.
The rule \rn{Conflict} recognizes when an equality and its negation both occur in $\Ec$, in which case $\Ec$ has no model.

\begin{figure}[t]
\centering
\begin{tabular}{c}
\rn{Cyclic}
\(
\inferrule{
  t : \tau
  \quad
  \tau \in \Data
  \quad
  %\ttpath{\Ec}{\ec{t}}{\ec{t}} \neq \emptyset
  \Val \ec{t} = \mu x. t'
  \quad
  x \in FV( t' )
}{
  \bot
}
\)
\\[3.7ex]
\rn{Bisimilar}
\(
\inferrule{
 t_1, t_2 : \tau
 \quad
 \tau \in \Codata
 \quad
 %\tpath{\Ec}{\ec{t_1}} = \tpath{\Ec}{\ec{t_2}}\sigma \neq \emptyset
 \Val \ec{t_1} \vsim \Val \ec{t_2}
}{
 \Ec := \Ec, t_1 \teq t_2
}
\)
\end{tabular}
\caption{Rules for cyclicity and bisimilarity.
}
\label{fig:ab-rules}
\end{figure}

\paragraph{Step 2: Apply cyclicity and bisimilarity.}
In this step,
we assume that $\Ec$ is saturated with respect to the rules in Figure~\ref{fig:cc-rules}, that is,
no non-redudant application of one of its rules can be applied to $\Ec$.
When this is the case, it is easy to see that $\Ec$ induces an equivalence relation over $\tEc$ such that two terms $t_1$ and $t_2$ are equivalent if and only if $t_1 \teq t_2 \in \Ec$.
Thus, we will in the following consider $\Ec$ as a set of equivalence classes of terms. 
For term $t \in \tEc$, we will write $\ec{t}$ to denote the equivalence class in $\Ec$ that containing $t$.

Recall that the $\mu$-notation can be used to represent (possibly cyclic) terms and values,
for instance, $\mu x. \const{C}( \const{0}, x )$ represents the cyclic value $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
Formally, we recursively define a $\mu$-term is either of the form
$\mu x. \const{C}( \vec t )$ for some constructor $\const{C} \in \Ctr$ and $\mu$-terms $\vec t$, 
or a variable $x$.
We assume all $\mu$-terms are \emph{well-typed}, which we defined recursively:
if the type of $\const{C}$ is $\vec \tau \rightarrow \upsilon$, 
then if $\vec v$ are well-type $\mu$-terms under the assumption that $x$ has type $\upsilon$,
then $\mu x. \const{C}( \vec v )$ is a well-typed term of type $\upsilon$.
We say a $\mu$-term is \emph{closed} if it contains no free variables.
We write $t \vsim s$ if $\mu$-terms $t$ and $s$ are syntactically equivalent modulo renaming of $\mu$-bound variables.
For convienience, we will use $\mu$-terms to refer to (classes of) values for both co-datatype and datatype terms,
where in the latter case, a $\mu$-term with a bound variable denotes an invalid term.
%where the latter case adds the restriction on $\mu$-terms $t$ that no subterms of $t$ contain are bound variables.

At the beginning of this step, 
we compute a mapping $\Val$ from equivalence classes to $\mu$-terms.
Informally, the terms mapped to by $\Val$ describe the (class of) values that terms in each equivalence class can take in the models of $\Ec$. 
For each equivalence class $\ec{x}$ of $\Ec$, we associate a fresh variable $v_{\ec{x}}$ of the same type as $x$ not occurring in $\tEc$,
and initially say that $\Val$ contains $\ec{x} \mapsto v_{\ec{x}}$ for each equivalence class $\ec{x}$ of $\Ec$ 
(in other words, there are initially no constraints on the values for terms).
Then, $\Val$ is updated by applying the following rule exhaustively:

\(
\inferrule{
  v_{\ec{x}} \in FV( \Val )
  \quad
  C( t_1, \ldots, t_n ) \in \ec{x}
  \quad
  C \in \Ctr
}{
  \Val := \Val \{ v_{\ec{x}} \mapsto \mu v_{\ec{x}}. C( v_{\ec{t_1}}, \ldots, v_{\ec{t_n}} ) \}
}
\)

Here, we write $FV( \Val )$ to denote the free variables occurring in $\Val$, which
excludes variables that occur beneath $\mu$-binders.
It is straightforward to show that the height of terms produced as a result of this rule
is bounded by the number of equivalence classes of $\Ec$,
our construction of $\Val$ is terminating.

\begin{example}
Say that $\Ec$ contains equivalence classes $\ec{x}$ and $\ec{y}$ where $\const{C}(z,x) \in \ec{y}$ and $\const{C}(w,y) \in \ec{x}$.
A possible sequence of applications of the above rule is shown below.
In the first column, we show the equivalence class that was considered,
and in the second column, we show the state of $\Val$.
\[\begin{array}{|l|@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l|}
\hline
\text{Eqc} & \multicolumn{3}{c}{\Val} & \ 
\\
\hline
& \{ & \ec{x} \mapsto v_{\ec{x}}, & \ec{z} \mapsto v_{\ec{z}}, & \\
&    & \ec{y} \mapsto v_{\ec{y}}, & \ec{w} \mapsto v_{\ec{w}} & \} \\
\ec{x}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, v_{\ec{y}} ), & \ec{z} \mapsto v_{\ec{z}}, & \\
&    & \ec{y} \mapsto v_{\ec{y}}, & \ec{w} \mapsto v_{\ec{w}} & \} \\
\ec{y}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ) ), & \ec{z} \mapsto v_{\ec{z}}, & \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ), & \ec{w} \mapsto v_{\ec{w}} & \} \\
\ec{x}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ) ), & \ec{z} \mapsto v_{\ec{z}}, & \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, v_{\ec{y}} ) ), & \ec{w} \mapsto v_{\ec{w}} & \} \\
\hline
\end{array}\]
In other words, the (class of) values for $v_{\ec{x}}$ in models of $\Ec$ 
is $\const{C}( v_{\ec{w}}, \const{C}( v_{\ec{z}}, \ldots ))$, 
and the class of values for $v_{\ec{y}}$ is $\const{C}( v_{\ec{z}}, \const{C}( v_{\ec{w}}, \ldots ))$,
where $v_{\ec{z}}$ and $v_{\ec{w}}$ are free variables.
$\Box$
\end{example}

Given $\Val$, the rules for cyclicity and bisimilar can be stated as follows, and are shown in Figure~\ref{fig:ab-rules}.
For cyclicity, if there is an equivalence class $\ec{t}$ of datatype type whose possible values $\mu x. t'$ are cyclic 
(as indicated by the assumption $x \in FV( t' )$),
then we can conclude that $\Ec$ is unsatisfiable.
For bisimilarity, if there are two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ 
of co-datatype type whose possible values $\Val \ec{t_1}$ and $\Val \ec{t_2}$ are equivalent modulo renaming of $\mu$-bound variables,
then we can conclude $t_1 \teq t_2$.
We demonstrate an application of this rule concretely with the following example.

\begin{example}
Let $\const{C}$ be a constructor of type $\tau_1 \times \tau_2 \rightarrow \tau_2$,
and let $\Ec$ be the set $\{ x \teq \const{C}(y,\const{C}(y,x)) \}$.
After applying the rules in Figure~\ref{fig:cc-rules} to completion, the equivalence classes of $\Ec$ are
$\{ x, \const{C}(y,\const{C}(y,x)) \}$, $\{ \const{C}(y,x) \}$, and $\{ y \}$.
Our construction of $\Val$ gives us:
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l}
\Val \ec{x} & = & 
\mu v_{\ec{x}}. \const{C}( v_{\ec{y}}, \mu v_{\ec{\const{C}(y,x)}}. \const{C}( v_{\ec{y}}, v_{\ec{x}} ) ) \\
\Val \ec{\const{C}(y,x)} & = & 
\mu v_{\ec{\const{C}(y,x)}}. \const{C}( v_{\ec{y}}, \mu v_{\ec{x}}. \const{C}( v_{\ec{y}}, v_{\ec{\const{C}(y,x)}} ) )
\end{array}\]
Notice that $\Val \ec{x}$ and $\Val \ec{\const{C}(y,x)}$ are syntactically equivalent for the renaming
$\{ v_{\ec{x}} \mapsto v_{\ec{\const{C}(y,x)}}, v_{\ec{\const{C}(y,x)}} \mapsto v_{\ec{x}} \}$,
and thus our calculus may infer the equality $x \teq \const{C}(y,x)$.
\qed
\end{example}

\begin{comment}
To explain the rules in Figure~\ref{fig:ab-rules}, we introduce the following notions.
First, an edge $\ec{t_1} \rightarrow^{C}_n \ec{t_2}$ is a transition between two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ 
(which we will call its \emph{source} and \emph{destination} respectively),
labeled by a constructor $C$ and integer $n$.
We say that edge $\ec{t_1} \rightarrow^{C}_n \ec{t_2}$ is \emph{induced by $\Ec$} if and only if $C( \vec u ) \in \ec{t_1}$ for some $\vec u$ and $\ec{t_2} = \ec{u_n}$.
In other words, $t_1$ is equivalent to a $C$-application whose $n^{th}$ argument is equivalent to $t_2$.
A \emph{path} $p$ is a non-empty ordered list of edges $e_1, \ldots e_n$ such that the destination of $e_i$ is the source of $e_{i+1}$ for $i = 1, \ldots (n-1)$,
and the sources of $e_1, \ldots, e_n$ are distinct.
We say that path $p$ is \emph{induced by $\Ec$} if and only if each of its edges are induced by $\Ec$.
Notice that since $\Ec$ contains a finite set of equivalence classes, all paths induced by $\Ec$ have finite length.
We call the \emph{source} of a path is the source of its first edge, and the \emph{destination} of a path is the destination of its last edge.
We say a path $p$ is \emph{maximal} if its destination $\ec{t}$ is either
the source of an edge in $p$, 
or does not contain an application of a non-nullary constructor (including the case when $t$ is not of datatype/codatatype type).
The set $\ttpath{\Ec}{\ec{t_1}}{\ec{t_2}}$ is the smallest set containing all maximal paths with source $\ec{t_1}$ and destination $\ec{t_2}$ that are induced by $\Ec$.
The set $\tpath{\Ec}{\ec{t_1}}$ is the union of $\ttpath{\Ec}{\ec{t_1}}{\ec{t_2}}$ for all $t_2 \in \tEc$.
We will write, for instance, $\ec{t_1} \rightarrow^{C_1}_{n_1} \ec{t_2} \rightarrow^{C_2}_{n_2} \ec{t_3}$ 
as shorthand for the path containing an edge from $\ec{t_1}$ to $\ec{t_2}$, followed by one from $\ec{t_2}$ to $\ec{t_3}$.
%A set of paths is \emph{disjoint} if it does not contain two paths $p_1$ and $p_2$ such that $p_1 = p_2 \sigma$ for some $\sigma$.

The rule \rn{Cyclic} recognizes when a path exists from an equivalence class $\ec{t}$ to itself, as indicated
by the assumption $\ttpath{\Ec}{\ec{t}}{\ec{t}} \neq \emptyset$.
In this case, $\Ec$ entails that $t$ contains itself as a (strict) subterm,
and thus if $t$ is a datatype, $\Ec$ must be unsatisfiable.
The rule \rn{Bisimilar} recognizes when two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ having co-datatype type are observationally equivalent.
In this rule, $\sigma$ is a complete mapping over the equivalence classes that occur as sources in the edges of paths in $\tpath{\Ec}{\ec{t_2}}$.
The rule applies if $\tpath{\Ec}{\ec{t_1}}$ is comprised of the paths $p \sigma$ for each (and only) the paths $p \in \tpath{\Ec}{\ec{t_2}}$,
in which case $t_1$ must be equal to $t_2$.
We demonstrate an application of this rule concretely with the following example.
\end{comment}

@@

\paragraph{Step 3: Branching}
\rem{Require : all co-datatypes either have infinite cardinality, or have cardinality 1.}

@@

\rem{Revise : now $\Val$ is constructed by calculus.}
Recall that the $\mu$-notation can be used to represent (possibly cyclic) values taken from an initial algebra, \rem{elaborate?} 
e.g. $\mu x. \const{C}( \const{0}, x )$ represents the infinite sequence $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
In this setting, a value can be viewed as a term-like structure where all subterms 
(which we will refer to as \emph{subvalues}) are either 
$\mu x. \const{C}( \vec v )$ for some constructor $\const{C}$ and subvalues $\vec v$
\footnote{We assume all values are well-typed. 
Here, the type of $\mu x. \const{C}( \vec v )$ and $x$ is the return type of $\const{C}$.}, or a variable $x$.
We will refer to values of this form as \emph{$\mu$-values}.
We say a $\mu$-value is \emph{closed} if it contains no free variables.
For convienience, we will represent the values of both datatypes and co-datatypes as closed $\mu$-values,
where the case of datatypes adds the restriction that none of its subvalues are variables.
